---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

Directory of model specifications and disaggregation specifications for these models.
The waste disaggregation specification files are the same as those founds in [useeior's diaggspecs](https://github.com/USEPA/useeior/tree/5e564aad45a528551288e25b95f009d1d761b841/inst/extdata/disaggspecs) and used in USEEIO v2.0.1-411, described in the [USEEIO v2.0 paper](https://www.nature.com/articles/s41597-022-01293-7), but are included here for convenience.

## Model Descriptions
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("R/utils.R")
library(useeior)
library(kableExtra)
```

```{r model-summary, include=FALSE}
model_specs <- list.files("model-specs")[endsWith(list.files("model-specs"), "GHG.yml")]
ModelSummary <- data.frame()
for (modelname in sub(".yml", "", model_specs)) {
  model <- useeior:::initializeModel(modelname,
                                     configpaths = paste0("model-specs/", modelname, ".yml"))
  model <- useeior:::loadIOData(model)
  df <- data.frame(t(c("Model Name" = modelname,
                       "# of Sectors" = ifelse(model$specs$CommodityorIndustryType=="Commodity",
                                               nrow(model$Commodities), nrow(model$Industries)),
                       "Commodity (C) or Industry (I)" = model$specs$CommodityorIndustryType,
                       "IO Data Year" = model$specs$IOYear,
                       "GHG and Economic Output Year" = model$specs$SatelliteTable$GHG$DataYears)),
                   check.names = FALSE)
  ModelSummary <- rbind(ModelSummary, df)
}
ModelSummary <- ModelSummary[order(ModelSummary[, "GHG and Economic Output Year"],
                                   ModelSummary[, "Commodity (C) or Industry (I)"]), ]
```

```{r model-summary-table}
options(knitr.table.format = "markdown")
kableExtra::kable(ModelSummary, row.names = FALSE, align = c("l", rep("r", ncol(ModelSummary)-1)))
```

The model specification files use the [useeior Model Specification format](https://github.com/USEPA/useeior/blob/master/format_specs/ModelSpecification.md) pertaining to the `useeior` release version that is being used to generate the factors.
